Wrinkling and yielding of protein gel

### 2013-09-10 poster_Rome.tex
Point @ 300Pa \dotsfill to see more clearly paragraphs

% see documentation for a0poster class for the size options here
\let\Textsize\normalsize
\def\Head#1{\noindent\hbox to \hsize{\hfil{\LARGE\color{Main}\raggedright\textsf{#1}}}\bigskip}
\def\LHead#1{\noindent{\LARGE #1}\smallskip}
\def\Subhead#1{\noindent{\large\color{Accent1}\textsc{#1}}}
\def\Title#1{\noindent{\VeryHuge\color{Accent2}\raggedright\textsf{#1}}}

% The textpos package is necessary to position textblocks at arbitary 
% places on the page.
\usepackage[absolute,overlay,showboxes
]{textpos}
% Set up the grid
%
% Note that [40mm,40mm] is the margin round the edge of the page --
% it is _not_ the grid size. That is always defined as 
% PAGE_WIDTH/HGRID and PAGE_HEIGHT/VGRID. In this case we use
% 15 x 25. This gives us a wide central column for text (7 grid
% spacings) and two narrow columns (3 each) at each side for 
% pictures, separated by 1 grid spacing.
%
% Note however that texblocks can be positioned fractionally as well,
% so really any convenient grid size can be used.
%
\TPGrid[40mm,40mm]{15}{25}  % 3 - 1 - 7 - 1 - 3 Columns

@@

@@

	\begin{tabular}{b{0.55\textwidth}b{0.45\textwidth}}
	\begin{tikzpicture}
	\begin{loglogaxis}[%
		ylabel={Breaking time (s)},ylabel near ticks,
		xlabel={Stress $\sigma$ (Pa)},
		xmin=10,
		legend style={font=\small\sc}, legend pos=south west,
		mark size={0.2em},
		]
		\addplot+[only marks, Accent1, mark options={fill=Accent1}] coordinates {(40, 67225) (50,29860) (100,398) (200,4)};
		\addplot+[only marks, Accent2, mark options={fill=Accent2}] table[x index=0, y index=1]{cas4_GDL1_t_cassure_sigma.txt};
		\legend{gdl 4\%, gdl 1\%};
		\addplot+[Accent1, no marks, forget plot, domain=40:200] gnuplot {6.32e+14*x^{-6.14}};
		\addplot+[Accent2, no marks, forget plot, domain=150:1000] gnuplot {3.93e+17*x^{-5.44}};
	\end{loglogaxis}
	\end{tikzpicture}&
	Irreversible fractures\linebreak
	\Subhead{Fracture\linebreak wavelength}
	\begin{itemize}
		\item stress-independent
		\item composition-indep.
		\item $\propto$ gap
	\end{itemize}\\
	\end{tabular}

@@

\textblockcolour{lightgray!50!white}
\TPMargin*{ 0.125\TPHorizModule }
\begin{textblock}{2.875}(12,2.625)%real width of 3
	\Head{Take away}
	\Subhead{A new kind of pattern}
	\begin{itemize}
		\item nested
		\item self generated
		\item boundary conditions
	\end{itemize}
	\Subhead{A good model for solids}
	\begin{itemize}
		\item Andrade creep over 6 decades in time
		\item Irreversible fractures
	\end{itemize}
	\Subhead{A link with fractures}
	\begin{itemize}
		\item Wrinkles can induce plasticity
		\item Wavelengths have the same dependence
		\item Detachment creates a free surface
		\item Fractures need complete overshoot
	\end{itemize}
\end{textblock}%Conclusion

>>>>

% see documentation for a0poster class for the size options here
\let\Textsize\normalsize
\def\Norulehead#1{\noindent\hbox to \hsize{\hfil\LARGE\textcolor{Main}{\textsf{#1}}}\bigskip}
\def\Head#1{\Norulehead{\dotfill #1}}
\def\LHead#1{\noindent{\LARGE #1}\smallskip}
\def\Subhead#1{\noindent{\large\color{Accent1}\textsc{#1}}}
\def\Title#1{\noindent{\VeryHuge\color{Accent2}\raggedright\textsf{#1}}}

% The textpos package is necessary to position textblocks at arbitary 
% places on the page.
\usepackage[absolute,overlay,%showboxes
]{textpos}
% Set up the grid
%
% Note that [40mm,40mm] is the margin round the edge of the page --
% it is _not_ the grid size. That is always defined as 
% PAGE_WIDTH/HGRID and PAGE_HEIGHT/VGRID. In this case we use
% 15 x 25. This gives us a wide central column for text (7 grid
% spacings) and two narrow columns (3 each) at each side for 
% pictures, separated by 1 grid spacing.
%
% Note however that texblocks can be positioned fractionally as well,
% so really any convenient grid size can be used.
%
\TPGrid[40mm,40mm]{15}{25}  % 3 - 1 - 7 - 1 - 3 Columns

@@

	\vspace{1em}

@@

	\begin{tabular}{b{0.55\textwidth}b{0.45\textwidth}}
	\begin{tikzpicture}
	\begin{loglogaxis}[%
		ylabel={Breaking time (s)},ylabel near ticks,
		xlabel={Stress $\sigma$ (Pa)},
		xmin=10,
		legend style={font=\small\sc}, legend pos=south west,
		mark size={0.2em},
		]
		\addplot+[only marks, Accent1, mark options={fill=Accent1}] coordinates {(40, 67225) (50,29860) (100,398) (200,4) (300,0.06)};
		\addplot+[only marks, Accent2, mark options={fill=Accent2}] table[x index=0, y index=1]{cas4_GDL1_t_cassure_sigma.txt};
		\legend{gdl 4\%, gdl 1\%};
		\addplot+[Accent1, no marks, forget plot, domain=40:300] gnuplot {9.2e+15*x^{-6.8}};
		\addplot+[Accent2, no marks, forget plot, domain=150:1000] gnuplot {3.93e+17*x^{-5.44}};
	\end{loglogaxis}
	\end{tikzpicture}&
	Irreversible fractures\linebreak
	\Subhead{Fracture\linebreak wavelength}
	\begin{itemize}
		\item stress-independent
		\item composition-indep.
		\item $\propto$ gap
	\end{itemize}\\
	\end{tabular}

@@

\textblockcolour{lightgray!50!white}
\TPMargin*{ 0.125\TPHorizModule }
\begin{textblock}{2.875}(12,2.625)%real width of 3
	\Norulehead{Take away}
	\Subhead{A new kind of pattern}
	\begin{itemize}
		\item nested
		\item self generated
		\item boundary conditions
	\end{itemize}
	\Subhead{A good model for solids}
	\begin{itemize}
		\item Andrade creep over 6 decades in time
		\item Irreversible fractures
	\end{itemize}
	\Subhead{A link with fractures}
	\begin{itemize}
		\item Wrinkles can induce plasticity
		\item Wavelengths have the same dependence
		\item Detachment creates a free surface
		\item Fractures need complete overshoot
	\end{itemize}
\end{textblock}%Conclusion
